%TCIDATA{LaTeXparent=0,0,thesis.tex}
                      

\chapter{Introduction}

\pagenumbering{arabic}

\section{Background and User Requirements}

The radar simulator (also called Sarsim2) described in this dissertation was
originally developed to produce \textit{synthetic range profiles} (SRPs) of
complex aircraft models. It was then expanded and upgraded to generate
simulated \textit{synthetic aperture radar} (SAR) data.

Over the last few years a substantial amount of work has been carried out by
the \textit{Radar Remote Sensing Group} (RRSG) at the \textit{University of
Cape Town }(UCT) to produce SRPs of aircraft targets using an L-Band search
radar of Reutech Systems \cite{Inggs:93, Inggs:92b, Richard4, Inggs:92a}.
The high range resolution that can be obtained from SRP processing makes it
feasible to extract characteristic features from a profile obtained from an
aircraft. The ultimate aim of producing SRPs is to use these extracted
features for\textit{\ non-cooperative target recognition} (NCTR), i.e.\ to
be able to identify an aircraft type from the echo signal received by the
radar \cite{Robinson}. The radar simulator was written to produce SRPs of
aircraft models, which could then be used to investigate the feasibility of
various aircraft-identification algorithms.

The stepped-frequency processing required to obtain SRPs of aircraft targets
has initiated further research in the RRSG into more efficient
stepped-frequency processing techniques \cite{Gill, Huang:96, Richard:97b,
Richard:97a, Ulander:98, Wehner}, and the radar simulator has been used
extensively to generate simulated data.

The RRSG group is also actively involved with SAR processing techniques \cite
{Crespo, Cumming, Hughes, Inggs:96, Mittermayer, Moreira:98, Runge}, and the
radar simulator has been invaluable in providing necessary simulation data
to test various processing algorithms.

\section{Simulator Features}

One of the main objectives of this simulator was to have an easy-to-use
graphical interface, which can show results in real-time. This requirement
makes it necessary to find some way of reducing the required computation.
The solution implemented may be called WYSIWIC (what you see is what is
calculated). This means that the data is only calculated to a resolution
depending on the screen resolution. Only when the data is saved to disk will
it be calculated and written with the required sampling rate. The exact
method will be explained in detail in Chapter~\ref{chapter:internals}.

Some of the features of the radar simulator include:

\begin{itemize}
\item  Chirp, monochrome and user-defined pulse modulations

\item  Stepped-frequency implementation with constant or user-defined
frequency increments

\item  Independent moving platforms with user-defined paths

\item  Generation of text script files

\item  Configurable A/D conversion

\item  Angle dependent \textit{radar cross section} (RCS) of point targets

\item  Rotating antennas, spot mode SAR

\item  Point target and platform motion errors

\item  All user-defined functions can be imported by a separate text file

\item  Powerful image viewer which can display SAR files of practically any
size
\end{itemize}

The program has been kept flexible so that features (for example using
real-life antenna gain patterns) can be loaded with ease.

\section{System requirements}

The graphical front-end of the simulator was initially written in C++ using
the \textit{Object Windows Library }(OWL) of Borland C++~5.0, but was then
rewritten with Borland C++ Builder, which made the development much easier.
Borland C++ Builder (BCB) can be considered as the best \textit{Rapid
Application Development }(RAD) tool currently available, offering visual
components combined with the flexibility and speed of C++. The simulator
exploits the protected memory model of 32 bit programs which has the
advantages of crash protection and practically no memory restrictions. It
therefore has to run under either Windows~95 or Windows~NT~4.0. For
portability reasons all the code (except the windows front end) has been
written in ANSI~C++. All processor intensive calculation routines have been
written as threads. This makes other tasks running in the background more
responsive and also enables the user to abort a calculation at any time.

A second program has been included, which is basically the same program
without the graphical front-end.. This program is portable as it is written
in pure ANSI~C++. It performs like a compiler which reads the script files
(text files) and writes the required simulation files to disk.

The simulator needs 16~Mb of RAM to work efficiently (32~Mb recommended with
Windows~NT), and it is recommended to use a graphics card displaying at
least 256~colours, but 65k is preferable. A screen resolution of 800 by 600
or higher is necessary.

The following files are required to run the radar simulator:

\begin{itemize}
\begin{enumerate}
\item  sarsim2.exe

\item  sarsimhlp.hlp

\item  sarsimhlp.gid
\end{enumerate}
\end{itemize}

The last two files are necessary to access online help. All the necessary 
\textit{dll} files have been linked into the executable. However if some of
the dialogs are displayed incorrectly when the simulator is executed, there
might be outdated libraries on the computer system. In this case copy the
files in the supplied \textbf{\TEXTsymbol{\backslash}dll} directory into the 
\textbf{\TEXTsymbol{\backslash}system32} subdirectory of the windows
directory.

The geometry setup and all simulation parameters are saved as a text file
with the extension ``scr''. External data files normally have the extension
``dat''. Note that long filenames and directory names are supported.

\section{Development of Dissertation}

This dissertation develops in the following way:

\begin{itemize}
\item  Chapter~\ref{chap:theory} gives a brief introduction to general radar
theory and discusses how this theory is applied in the radar simulator.

\item  Chapter~\ref{chapter:start} introduces the radar simulator by setting
up and going through a very simple simulation.

\item  Chapter~\ref{chapter:commands} gives a complete description of all
windows and dialogs appearing in Sarsim2.

\item  The structure of the script files is explained in Chapter~\ref
{chapter:script}. Script files can be used to automate certain tasks. They
are effectively text files containing a description of the simulation setup.

\item  In Chapter~\ref{chapter:internals} the formulas used in Sarsim are
described in detail.

\item  Chapter~\ref{chapter:examples} describes various examples for
different applications.

\item  Chapter~\ref{chapter:concl} summarises conclusions reached and
discusses future work.

\item  Appendix~\ref{app:examples} describes various simulation examples to
illustrate the functioning of the radar simulator. This work has been
co-authored by Helvin Gunputh.
\end{itemize}
